### 2018-09-15 sections/objects.tex
Implemented remaining replies to CDS comments from Jason Nielsen
Reverting to old description of OL. Need to fix for tautau

Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

In the $\Hbb$ search, overlaps between candidate objects are removed sequentially, following this order: muons, electrons and jets. Firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. Overlaps between electron and jet candidates are resolved 
next, and finally, overlaps between remaining jet candidates and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapped second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.

>>>>

Hadronically decaying $\tau$-lepton ($\tauhad$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\tauhad$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\tauhad$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\tauhad$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-quark/gluon jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\tauhad$ candidates are removed via a BDT trained to reject electrons.
Any $\tauhad$ candidate that is also $b$-tagged is rejected.

Overlaps between candidate objects are removed sequentially, following this order: muons, electrons,
$\tauhad$ (only for the $\Htautau$ search), and jets. In the $\Hbb$ search, firstly, electron candidates that lie 
within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
In the $\Htautau$ search, a fixed cone size of $\Delta R=0.2$ is used to determine the overlap between
candidate objects, and only the highest-$\pt$ (leading) or the two leading $\tauhad$ candidates (depending on the
analysis channel, see Section~\ref{sec:data_presel}) are considered to resolve their overlap with jets.

% TEXT FROM BOYANG. NEED TO RECHECK WHAT WE HAVE ABOVE IS ACCURATE
%In the $\Hbb$ search, overlaps between candidate objects are removed sequentially, following this order: muons, electrons and jets. Firstly, electron candidates that lie within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. Overlaps between electron and jet candidates are resolved 
%next, and finally, overlaps between remaining jet candidates and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
%The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
%that are likely to have arisen in the decay chain of hadrons and to retain the overlapping jet instead. 
%Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
%and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
%few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
%if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
%In the $\Htautau$ search, the objects are removed with the following sequence: if two electrons have overlapping second-layer cluser, or shared tracks, the electron with lower $\pt$ is removed; $\tauhad$ within a $\Delta R=0.2$ cone of an electron or muon are removed; if a muon sharing an ID track with an electron and the muon is calo-tagged, the muon is removed, otherwise the electron is removed; jets within a $\Delta R=0.2$ cone of an electron are removed; electrons within a $\Delta R=0.4$ cone of a jet are removed; when a muon ID track is ghost associated to a jet or within a $\Delta R=0.2$ cone of a jet, the jet is removed if it has less than 3 tracks with $\pt>500$ MeV or has a relative small $\pt$ ($\pt^{\mu}>0.5\pt^{\text{jet}} \text{ and } \pt^{\mu}>0.7[\text{the scalar sum of the } \pt \text{'s of the jet tracks with } \pt>500$ MeV]); muons within a $\Delta R=0.4$ cone of a jet are removed; jets within a $\Delta R=0.2$ cone of the leading $\tauhad$ ($\lephad$), or with the two leading $\tauhad$'s ($\hadhad$), are removed.
